Consistency scores in text data

### 2020-08-05 outputs/documents/paper.Rmd
implementations on Word2Vec and GloVe, WIP

**(Ke-Li add brief write-up of implementation in R please.)**
#### Notes ####
CBOW might be better for text cleaning because it uses the context to predict the center word.

@@

**(Ke-Li add brief paragraph about negatives of this approach.)**
#### Notes not content ####
- Inability to handle unknown or out-of-vocabulary (OOV) words.
- No shared representations at sub-word levels
- Word presentations are not contextual. Representation of apple is the same in context of fruit and tech company
- [Although these pre-trained embeddings can capture semantic meanings of words, they are context-free and fail to capture higher-level concepts in context, such as polysemous disambiguation, syntactic structures, semantic roles, anaphora.] (@hanretty2018comparing).

**(Ke-Li add brief write-up of implementation in R please.)** 
GloVe word embedding is available to operate in R with the text2vec package developed by Dmitriy Selivanov **(Ke-Li add package citation)**.

>>>>

**(Ke-Li add brief write-up of implementation in R please.)**
There are a few packages for implementing a Word2Vec model in R. The packages are "rword2vec" by Mukul Chaware and "word2vec" by Jan Wijffels, BNOSAC, and Max Fomichev. Both packages uses the same algorithm that Word2Vec uses to produce word representations, but they do not have an affiliation with Google. Another way to implement a Word2Vec model in R is through Keras package. Keras is an API for deep learning written in Python (@chollet2015keras) and the Keras package provides an R interface to Keras **(Ke-Li add citation for the package)**. RStudio published a tutorial for implementing the skip-gram model of Word2Vec (@falbel2017word); we intend to follow this tutorial as the approach to implement a Word2Vec model.

@@

**(Ke-Li add brief paragraph about negatives of this approach.)**
**(This limitation paragraph applies to both Word2Vec and GloVe)**
As @hanretty2018comparing point out, although word embedding models can capture semantic means of words, "they are context-free and fail to capture higher-level concepts in context, such as polysemous disambiguation, syntactic structures, semantic roles, anaphora". Word embedding models do not represent a homonyms that has difference meanings in different vectors depending on the context. For example, "squash" can be a type of hard shelled vegetable or can be referring to a racket and ball sport, but there is only one series of vectors to represent the word "squash", instead of dynamically changing the vectors depending on the context. Moreover, from our observation, the word embedding models are unable to handle novel words that are not included in the vocabulary of the training corpus; for this reason, we conclude that the generalizability of word embedding models is sub-optimal.

There are more than one way to implement GloVe word embedding model in R. One way is to load GloVe embeddings into a frozen Keras Embedding layer **(Keli add citation to the blog post by Keras)** using the Keras R package (**(Keli add citation to package)**). Another way, as mentioned and briefly demonstrated by Rstudio in their blog post, is to use the "text2vec" package developed by Dmitriy Selivanov **(Ke-Li add package citation)**.
